%\special{pdf:encrypt ownerpw (hymns) userpw (ited) length 128 perm 2052}

\RequirePackage{silence} % :-\
    \WarningFilter{scrreprt}{Usage of package `titlesec'}
    %\WarningFilter{scrreprt}{Activating an ugly workaround}
    \WarningFilter{titlesec}{Non standard sectioning command detected}
\documentclass[ twoside,openright,titlepage,numbers=noenddot,%1headlines,
                headinclude,footinclude,cleardoublepage=empty,abstract=on,
                BCOR=5mm,paper=a4,fontsize=11pt
                ]{scrreprt}

%********************************************************************
% Note: Make all your adjustments in here
%*******************************************************
\input{Configurations/classicthesis-config}

%********************************************************************
% Bibliographies
%*******************************************************
\addbibresource{Bibliography/main.bib}
\addbibresource[label=ownpubs]{Bibliography/own.bib}

\begin{document}
\frenchspacing
\raggedbottom
\selectlanguage{american} % american ngerman
%\renewcommand*{\bibname}{new name}
%\setbibpreamble{}
\pagenumbering{roman}
\pagestyle{plain}

%********************************************************************
% Frontmatter
%*******************************************************
%\include{FrontBackmatter/DirtyTitlepage}
\include{FrontBackmatter/Titlepage}
\include{FrontBackmatter/Titleback}
\cleardoublepage\include{FrontBackmatter/Dedication}
%\cleardoublepage\include{FrontBackmatter/Foreword}
\cleardoublepage\include{FrontBackmatter/Abstract}
\cleardoublepage\include{FrontBackmatter/Publications}
\cleardoublepage\include{FrontBackmatter/Acknowledgments}
\cleardoublepage\include{FrontBackmatter/Contents}

%********************************************************************
% Mainmatter
%*******************************************************
\cleardoublepage
\pagestyle{scrheadings}
\pagenumbering{arabic}

\cleardoublepage
\ctparttext{Introduction to the concepts needed to understand the motivation behind the experiment, the functioning of the detector and techniques used. Description of the detection system. Proposed scientific and industrial applications for the detector system.}
\part{Introduction \& Theory}\label{pt:intro}
\cleardoublepage

\include{Chapters/Part1/Chapter01.tex}

\include{Chapters/Part1/Chapter02.tex}

\include{Chapters/Part1/Chapter03.tex}

\cleardoublepage
\ctparttext{Data-driven upgrades of the multi \ac{i-TED} detector system. In this part, the components and parameters which were decreased the system's performance were identified and were either replaced, in case of components, of optimized, in case of the parameters. For the case of parameters, the conditions of use of the system were taken into account since the optimization can depend on the use case.}
\part{Detector upgrades}\label{pt:detector}
\cleardoublepage

\include{Chapters/Part2/Chapter04.tex}

\include{Chapters/Part2/Chapter05.tex}

\cleardoublepage
\ctparttext{Comparison of the imaging techniques for Compton cameras. Analysis of the performance of classical and machine learning techniques for background discrimination based on the two main parameters: number of total peak events and signal-to-background ratio.}
\part{Imaging and background discrimination}\label{pt:approaches}
\cleardoublepage

\include{Chapters/Part3/Chapter06.tex}

% ********************************************************************
% Backmatter
%*******************************************************
\appendix
%\renewcommand{\thechapter}{\alph{chapter}}
\cleardoublepage
\part{Appendix}
\include{Chapters/Appendix/Chapter0A.tex}
\include{Chapters/Appendix/Chapter0B.tex}
\include{Chapters/Appendix/Chapter0C.tex}
%********************************************************************
% Other Stuff in the Back
%*******************************************************
\cleardoublepage\include{FrontBackmatter/Bibliography}
%\cleardoublepage\include{FrontBackmatter/Declaration}
% ********************************************************************
% Game Over: Restore, Restart, or Quit?
%*******************************************************
\end{document}
% ********************************************************************
