%************************************************
%************************************************
%************************************************
\chapter{Applications}\label{ch:applications}
%************************************************
%************************************************
%************************************************

%************************************************
%************************************************
\section{Scientific Applications}
%************************************************
%************************************************

%************************************************
\subsection{Neutron captures of astrophysical interest}
%************************************************

The main purpose of the \ac{i-TED} detector system is its application to nucleosynthesis studies.

As previously in \ref{ch:background}, the imaging capabilities of the detector allow for the selection of events based of their spacial origin. This results in an improvement of the peak-to-background ratio, allowing more precise measurements of the neutron capture cross-sections.

The cross-section of the neutron capture are of interest for nuclear astrophysics because the abundance of elements in a start, and by extension its evolution, depend on the cross-section of different nuclei that form it.

There are many cases where more precise measurements are needed in order to explain discrepancies between current theoretical models and the measured relative abundances of elements in the universe.

%************************************************
%************************************************
\section{Industrial Applications}
%************************************************
%************************************************

%************************************************
\subsection{Dose monitoring in hadron therapy}
%************************************************

\begin{itemize}
    \item SYNERGY4HT
    \begin{itemize}
        \item Using imaging capabilities for studying the range in tissue
        \item To be used for cancer treatment 
        \item The energy deposition is mostly at the very end of the path (Bragg's peak)
        \item Generates prompt g that are then detected by i-TED by compton imaging
        \item Also allows the use of PET by selecting only 511keV events in one detector in opposite deteectors
    \end{itemize}
    \item Compton vs PET
    \begin{itemize}
        \item PET provides better image resolution
        \item PET is an easier technique
        \item PET is performed either between bunches (for short lived [ms] isotopes) or in a dedicated PET scanner (for longer lived [min] isotopes)
        \item Compton provides much more counts (uses different energies, PET only uses the 511keV from anhilation)
        \item Compton uses prompt g-rays occuring in the vicinity of the Bragg peak
        \item PET occurs in the anhilation of B-radiation emitted by an isotope, being correlated to the Bragg peak but not easily identifyable from data without simulations or just providing relative measurements of the range
        \item Providing both Compton and PET, i-TED can be used to improve MC simulations thar relate the PET range spectrum to the Bragg peak
    \end{itemize}
\end{itemize}

%************************************************
\subsection{Nuclear waste analysis}
%************************************************

One increasingly common application for imaging detectors is the analysis of nuclear waste.

In many cases the nuclear waste, specially that which is highly radioactive, doesn't have the same level of radioactivity throughout the whole material. More commonly, waste classified as having a higher level of radiation is composed of a smaller very radioactive portion and a bigger less radioactive portion. 

The use of imaging capabilities allows the identification of more problematic parts of the waste that can be separated, treated and stored according to the respective procedures without treating the whole waste as a monolith. This has significant improvements in terms of storage space and cost of treatment.

%\begin{itemize}
%    \item Victor's PhD
%    \begin{itemize}
%        \item Using i-TED for this application
%        \item Data collected on the reaction 80Se(n,g)
%        \item Data being discussed with theoreticians
%    \end{itemize}
%    \item Application to ESARDA 2023 - Nuclear Safeguards and Non Proliferation
%    \begin{itemize}
%        \item https://esarda.jrc.ec.europa.eu/events/21st-esarda-course-2023-04-24_en
%        \item Applied on Feb 6th - Waiting
%        \item Course online on 24 - 28 April, 2023
%        \item 3 ECTS
%    \end{itemize}
%\end{itemize}